One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
more BinoX results and plots
new calibration plots
edit, and adition of citation

A limiting factor of GEA is the pathway definition databases. While \url{http://pathguide.org} list 708 databases of pathway definitions\cite{bader2006pathguide},  some critique has been voiced concerning the completeness and rigor of current pathway databases. Hence efforts have been directed to designing methods that extend the pathway definitions, by functional association networks, like STRING\cite{szklarczyk2014string}. Instead of directly examining the overlap between the query and pathway sets, one can evaluate the number of links in the functional association network that connect the query and pathway set\cite{alexeyenko2012network, glaab2012enrichnet, mccormack2013statistical, ogris2016novel, signorelli2016neat}. This is known as Network Enrichment Analysis (NEA).

>>>>

A limiting factor of GEA is the pathway definition databases. While \url{http://pathguide.org} list 708 databases of pathway definitions\cite{bader2006pathguide},  some critique has been voiced concerning the completeness and rigor of current pathway databases. Hence efforts have been directed to designing methods that extend the pathway definitions, by functional association networks, like STRING\cite{szklarczyk2014string} and FunCoup\cite{ogris2017funcoup}. Instead of directly examining the overlap between the query and pathway sets, one can evaluate the number of links in the functional association network that connect the query and pathway set\cite{alexeyenko2012network, glaab2012enrichnet, mccormack2013statistical, ogris2016novel, signorelli2016neat}. This is known as Network Enrichment Analysis (NEA).
